Descriptive Complexity for Counting Complexity Classes

### 2017-03-08 LMCS/saluja.tex
journal 8 mar

\begin{figure*}
%\begin{center}
%\begin{tikzpicture}
%\node[rectw] (n1) {$\E{0}$};
%\node[rectw, right=0.5cm of n1] (n2) {};
%\node[rectw, above=0.3cm of n2] (n3) {$\E{1}$}
%	edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n1);
%\node[rectw, below=0.3cm of n2] (n4) {$\QE{0}$}
%        edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n1);
%\node[rectw, right=0.3cm of n2] (n5) {$\QE{1}$}
%        edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n3)
%         edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n4);
%\node[rectw, right=0.3cm of n5] (n6) {$\U{1}$}       
%        edge[draw=white] node {$\subsetneq$} (n5);
%\node[rectw, right=0.3cm of n6] (n7) {$\QU{1}$}       
%        edge[draw=white] node {$=$} (n6);
%\node[rectw, right=0.3cm of n7] (n8) {$\E{2}$}       
%        edge[draw=white] node {$\subsetneq$} (n7);
%\node[rectw, right=0.3cm of n8] (n9) {$\QE{2}$}       
%        edge[draw=white] node {$=$} (n8);        
%\node[rectw, right=0.3cm of n9] (n10) {$\U{2}$}       
%        edge[draw=white] node {$\subsetneq$} (n9);
%\node[rectw, right=0.3cm of n10] (n11) {$\QU{2}$}       
%        edge[draw=white] node {$=$} (n10); 
%\node[rectw, right=0.3cm of n11] (n12) {$\sfo$}       
%        edge[draw=white] node {$=$} (n11); 
%\end{tikzpicture}
%\end{center}
\begin{center}
	\begin{tikzpicture}
	\node[rectw] (n1) {$\E{0}$};
	\node[rectw, right=0.5cm of n1] (n2) {};
	\node[rectw, above=0.3cm of n2] (n3) {$\E{1}$}
		edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n1);
	\node[rectw, below=0.5cm of n2] (n4) {$\QE{0}$}
		edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n1);
	\node[rectw, right=0.5cm of n2] (n5) {$\QE{1}$}
		edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n3)
		edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n4);
	\node[rectw, right=0.8cm of n5] (n6) {$\U{1}$}       
		edge[draw=white] node {$\subsetneq$} (n5);
	\node[rectw, below=0.3cm of n6] (n7) {$\QU{1}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n6);
	\node[rectw, right=1.0cm of n6] (n8) {$\E{2}$}       
		edge[draw=white] node {$\subsetneq$} (n6);
	\node[rectw, below=0.3cm of n8] (n9) {$\QE{2}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n8);        
	\node[rectw, right=1.0cm of n8] (n10) {$\U{2}$}       
		edge[draw=white] node {$\subsetneq$} (n8);
	\node[rectw, below=0.3cm of n10] (n11) {$\QU{2}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n10); 
	\node[rectw, right=0.5cm of n10] (n12) {$\sfo$}       
		edge[draw=white] node {$=$} (n10); 
	\end{tikzpicture}
\end{center}
\vspace{-0.4cm}
\caption{The relationship between the $\sfo$-hierarchy and the $\eqso(\fo)$-hierarchy, where $\E{1}$ and $\QE{0}$ are incomparable. \label{fig-sfo-eqso}}
\vspace{-0.1cm}
\end{figure*}

>>>>

\begin{figure*}
%\begin{center}
%\begin{tikzpicture}
%\node[rectw] (n1) {$\E{0}$};
%\node[rectw, right=0.5cm of n1] (n2) {};
%\node[rectw, above=0.3cm of n2] (n3) {$\E{1}$}
%	edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n1);
%\node[rectw, below=0.3cm of n2] (n4) {$\QE{0}$}
%        edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n1);
%\node[rectw, right=0.3cm of n2] (n5) {$\QE{1}$}
%        edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n3)
%         edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n4);
%\node[rectw, right=0.3cm of n5] (n6) {$\U{1}$}       
%        edge[draw=white] node {$\subsetneq$} (n5);
%\node[rectw, right=0.3cm of n6] (n7) {$\QU{1}$}       
%        edge[draw=white] node {$=$} (n6);
%\node[rectw, right=0.3cm of n7] (n8) {$\E{2}$}       
%        edge[draw=white] node {$\subsetneq$} (n7);
%\node[rectw, right=0.3cm of n8] (n9) {$\QE{2}$}       
%        edge[draw=white] node {$=$} (n8);        
%\node[rectw, right=0.3cm of n9] (n10) {$\U{2}$}       
%        edge[draw=white] node {$\subsetneq$} (n9);
%\node[rectw, right=0.3cm of n10] (n11) {$\QU{2}$}       
%        edge[draw=white] node {$=$} (n10); 
%\node[rectw, right=0.3cm of n11] (n12) {$\sfo$}       
%        edge[draw=white] node {$=$} (n11); 
%\end{tikzpicture}
%\end{center}
\begin{center}
	\begin{tikzpicture}
	\node[rectw] (n1) {$\E{0}$};
	\node[rectw, right=0.5cm of n1] (n2) {};
	\node[rectw, above=0.3cm of n2] (n3) {$\E{1}$}
		edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n1);
	\node[rectw, below=0.5cm of n2] (n4) {$\QE{0}$}
		edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n1);
	\node[rectw, right=0.5cm of n2] (n5) {$\QE{1}$}
		edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n3)
		edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n4);
	\node[rectw, right=0.8cm of n5] (n6) {$\U{1}$}       
		edge[draw=white] node {$\subsetneq$} (n5);
	\node[rectw, below=0.3cm of n6] (n7) {$\QU{1}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n6);
	\node[rectw, right=1.0cm of n6] (n8) {$\E{2}$}       
		edge[draw=white] node {$\subsetneq$} (n6);
	\node[rectw, below=0.3cm of n8] (n9) {$\QE{2}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n8);        
	\node[rectw, right=1.0cm of n8] (n10) {$\U{2}$}       
		edge[draw=white] node {$\subsetneq$} (n8);
	\node[rectw, below=0.3cm of n10] (n11) {$\QU{2}$}       
		edge[draw=white] node {\rotatebox{90}{$=$}} (n10); 
	\node[rectw, right=0.5cm of n10] (n12) {$\sfo$}       
		edge[draw=white] node {$=$} (n10); 
	\end{tikzpicture}
\end{center}
\vspace{1cm}
\begin{center}
	\begin{tikzpicture}
	\node[rectw] (n1) {$\E{0}$};
	\node[rectw, right=1.2cm of n1] (n2) {};
	\node[rectw, above=0.2cm of n2] (n3) {$\E{1}$}
	edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n1);
	\node[rectw, below=0.1cm of n2] (n4) {$\QE{0}$}
	edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n1);
	\node[rectw, right=1.2cm of n2] (n5) {$\QE{1}$}
	edge[draw=white] node {\rotatebox{315}{$\subsetneq$}} (n3)
	edge[draw=white] node {\rotatebox{45}{$\subsetneq$}} (n4);
	\node[rectw, right=1.3cm of n5] (n6) {\rotatebox{90}{$=$}}       
	edge[draw=white] node {$\subsetneq$} (n5);
	\node[rectw, above=0cm of n6] (n13) {$\U{1}$};
	\node[rectw, below=0cm of n6] (n7) {$\QU{1}$};      
	\node[rectw, right=1.8cm of n6] (n8) {\rotatebox{90}{$=$}}       
	edge[draw=white] node {$\subsetneq$} (n6);
	\node[rectw, above=0cm of n8] (n14) {$\E{2}$};
	\node[rectw, below=0cm of n8] (n9) {$\QE{2}$};       
	\node[rectw, right=1.8cm of n8] (n10) {\rotatebox{90}{$=$}}       
	edge[draw=white] node {$\subsetneq$} (n8);
	\node[rectw, above=0cm of n10] (n15) {$\U{2}$};
	\node[rectw, below=0cm of n10] (n11) {$\QU{2}$};      
	edge[draw=white] node {\rotatebox{90}{$=$}} (n10); 
	\node[rectw, right=0.5cm of n10] (n12) {$\sfo$}       
	edge[draw=white] node {$=$} (n10); 
	\end{tikzpicture}
\end{center}
\vspace{-0.4cm}
\caption{The relationship between the $\sfo$-hierarchy and the $\eqso(\fo)$-hierarchy, where $\E{1}$ and $\QE{0}$ are incomparable. \label{fig-sfo-eqso}}
\vspace{-0.1cm}
\end{figure*}
